Balsa: A Compact Line Notation Based on SMILES

### 2022-07-02 manuscript.tex
Adds cyclooctatetraene figure. Closes #13.

Cyclic conjugated polyenes present special challenges to the use of PPBs, as exemplified by cyclooctatetraene. Although the (\textit{anti}, \textit{anti}, \textit{anti}, \textit{anti}) conformation is expressable, the (\textit{syn}, \textit{anti}, \textit{anti}, \textit{anti}) conformation is not. This problem arises because the same PPB encodes partial parity for two different double bonds.

\begin{figure}
    \centering
    \includegraphics{filler}
    \caption{Cyclooctatetraene. Some double bond conformations are not expressable.}
    \label{fig:cyclooctatetraene}
\end{figure}

>>>>

Cyclic conjugated polyenes present special challenges to the use of PPBs, as exemplified by cyclooctatetraene (Figure~\ref{fig:cyclooctatetraene}). Although the (\textit{anti}, \textit{anti}, \textit{anti}, \textit{anti}) conformation is expressable, the (\textit{syn}, \textit{anti}, \textit{anti}, \textit{anti}) conformation is not. This problem arises because the conformation for two different double bonds is set by the same PPB.

\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{cyclooctatetraene.pdf}
    \caption{Cyclooctatetraene. The all-(\textit{Z}) conformation is expressable (left), but the (\textit{Z},\textit{Z},\textit{Z},\textit{E}) conformation is not (right). Although the local conformations for the latter are all valid, the global conformation introduces a conflict, the direction marked in red.}
    \label{fig:cyclooctatetraene}
\end{figure}
